Co-methylation

### 2015-04-21 Rmarkdown/comethylation.Rmd
Plan of attack for finishing co-methylation chapter.

>>>>

## Plan of attack

Following discussion with Terry (2015-04-21), this is my plan of attack to finish this chapter and the `methsim` chapter.

- Read up on what happens with the MH estimator when the common odds ratio assumption is invalid.
  - Is there a better estimator in this setting? The Miettennen estimator?
- Demonstrate via simulation that the unconditional LOR estimator applied to $2 \times 2$ tables is biased when $d$ is small and the marginal probabilities are near the boundaries.
  - Corrollary: Don't use the LOR estimates of within-fragment co-methylation from individual $2\times 2$ tables. I know they're biased, so there's no reason to show these results.
- Demonstrate that the MH estimator applied to $2 \times 2 \times K$ tables is unbiased when $d$ is small (per-table) and the marginal probabilities are near the boundaries.
  - Need to investigate the setting where the marginal probabilities are heterogeneous across the $K$ tables but with the same odds-ratio.
  - Need to investigate the setting where the odds ratio __is not__ common to the $K$ tables; what does the MH estimator end up estimating?
- Compute MH estimates (and standard errors) of within-fragment co-methylation for different stratification strategies.
  - Stratify by IPD
  - Stratify by IPD + chromosome
  - Stratify by IPD + chromosome + chromosome arm
  - Stratify by IPD + chromosome + chromosome arm + bin (Mb)
  - Check whether the more-stratified estimates fall within a reasonable distance from the less-stratified estimates (i.e., with respect to standard errors of the less-stratified estimates).
- Settle on the most appropriate level of stratification and apply to all samples.
  - Discuss results.
- `methsim`: Sample LORs from a Normal(mu, sigma^2) distribution, where mu (resp. sigma) is the MH estimator (resp. standard error? empirical variance of stratified MH estimators?) of within-fragment co-methylation for that IPD and region-type.
